Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-05 paper.qmd
Updated Figure 6

```{r}
#| echo: false
#| label: fig-bins-two-curvy
#| fig-pos: H
#| fig-cap: "Hexbin density plots of tSNE layout of the non-linear cluster data, using three different bin inputs: (a) $b = 240/98 \\text{ } (15, \\text{ }16)$, (b) $b = 528/173 \\text{ } (22, \\text{ }24)$, and (c) $b = 2496/549 \\text{ } (48, \\text{ }52)$. Color indicates standardized counts, dark indicating high count and light indicates low count. At the smallest bin size, the data structure is discontinuous, suggesting that there are too many bins. Using the MSE of the model fit in $7\\text{-}D$ helps decide on a useful choice of number of bins."
#| fig-width: 9
#| fig-height: 3

@@

- the choice of NLDR method, and the parameters used to create it, and
- model fit parameters: bin size, low density bin removal, long edge removal.

>>>>

```{r}
#| echo: false
#| label: fig-bins-two-curvy
#| fig-pos: H
#| fig-cap: "Hexbin density plots of tSNE layout of the non-linear cluster data, using three different bin inputs: (a) $b = 240/98 \\text{ } (15, \\text{ }16)$, (b) $b = 720/215 \\text{ } (24, \\text{ }30)$, and (c) $b = 2496/549 \\text{ } (48, \\text{ }52)$. Color indicates standardized counts, dark indicating high count and light indicates low count. At the smallest bin size, the data structure is discontinuous, suggesting that there are too many bins. Using the MSE of the model fit in $7\\text{-}D$ helps decide on a useful choice of number of bins."
#| fig-width: 9
#| fig-height: 3

@@

- the choice of NLDR method, and the parameters used to create it, and
- model fit parameters: bin size, low density bin removal.
